%% This list is at the bottom of the Sample Pattern file - if you add any records to this glossary please add it there as well


%%%
% Simple Stitches
%%%

\newglossaryentry{K}{name={K},description={Knit}}

\newglossaryentry{P}{name={P},description={Purl}}

%%%
% Increases
%%%

\newglossaryentry{YO}{name={YO},description={Yarn over}}

\newglossaryentry{M1Loop}{name={M1},description={Backward Loop Make 1 - Twist the working yarn to make a loop, and put the loop on the working needle}}

\newglossaryentry{M1L}{name={M1L},description={Left Leaning Make 1 - Using the non-working needle, lift the strand that runs between needles, from the front. Work the picked up strand through the back loop}}

\newglossaryentry{M1R}{name={M1R},description={Right Leaning Make 1 - Using the non-working needle, lift the strand that runs between needles, from the back. Work the picked up strand}}

%%%
% Decreases
%%%

\newglossaryentry{K2tog}{name={K2tog},description={Knit two stitches together}}

\newglossaryentry{SSK}{name={SSK},description={Slip one stitch as if to knit, slip a second stitch as if to knit. Insert your left needle tip into both stitches and knit the two stitches together through the back loop}}

\newglossaryentry{P2tog}{name={P2tog},description={Purl two stitches together}}

\newglossaryentry{SSP}{name={SSP},description={Slip 2 stitches knitwise. Move them back to the LH needle and purl them together through the back loop}}

%%%
%Cables
%%%

\newglossaryentry{2/2LC}{name={2/2LC},description={Slip two stitches onto the cable needle. Holding the cable needle in front of your work, knit the next two stitches. Then knit the two stitches off the cable needle}}

\newglossaryentry{2/2RC}{name={2/2RC},description={Slip two stitches onto the cable needle. Holding the cable needle in back of your work, knit the next two stitches. Then knit the two stitches off the cable needle}}

\newglossaryentry{2/1LC}{name={2/1LC},description={Slip two stitches onto the cable needle. Holding the cable needle in front of your work, knit the next stitch. Then knit the two stitches off the cable needle}}

\newglossaryentry{2/1RC}{name={2/1RC},description={Slip one stitch onto the cable needle. Holding the cable needle in back of your work, knit the next two stitches. Then knit the one stitch off the cable needle}}

\newglossaryentry{1/2LC}{name={1/2LC},description={Slip one stitch onto the cable needle. Holding the cable needle in front of your work, knit the next two stitches. Then knit the one stitch off the cable needle}}

\newglossaryentry{1/2RC}{name={1/2RC},description={Slip two stitches onto the cable needle. Holding the cable needle in back of your work, knit the next one stitch. Then knit the two stitches off the cable needle}}

\newglossaryentry{1/1LC}{name={1/1LC},description={Slip one stitch onto the cable needle. Holding the cable needle in front of your work, knit the next stitch. Then knit the stitch off the cable needle}}

\newglossaryentry{1/1RC}{name={1/1RC},description={KSlip one stitch onto the cable needle. Holding the cable needle in back of your work, knit the next stitch. Then knit the stitch off the cable needle.}}


%%%
% Slipped Stitches
%%%

\newglossaryentry{S1}{name={S1},description={On the right side, slip one stitch as if to purl with working yarn in back. On the wrong side, slip one stitch as if to purl, with working yarn in front}}
